%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Backend Engineer} % Job title
    {Practice Ignition} % Organization
    {Sydney, Australia} % Location
    {Apr. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented direct debit payment for customers in the UK, Australia and Canada using Stripe. This helps to increase customer base by 30\%.}
        \item {Built and designed the integration with Zapier using OAuth2. This allows Practice Ignition to integrate with 3000+ apps.}
        \item {Built a solution to automate the payment dispute handling process.}
        \item {Implemented GraphQL to replace legacy REST endpoints.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Full Stack Developer} % Job title
    {RateCity} % Organization
    {Sydney, Australia} % Location
    {Jan. 2015 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the main application infrastructure migration from managed hosting to Amazon AWS utilizing Ansible ( Infrastructure as Code tool ).}
        \item {Implemented an A/B testing system using HAProxy. It allows product team to run experiments and track the performance of new features.}
        \item {Worked with cross functional teams to migrate two applications from Ruby on Rails to NodeJS, React and Elasticsearch.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Captiv8} % Organization
    {Sydney, Australia} % Location
    {May. 2012 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and deployed various digital campaigns and Facebook microsites using PHP and Amazon AWS.}
        \item {Built and designed a custom queueing system for Bundaberg Limited Bottle release event.}
        \item {Designed and implemented a video content distribution system to be used in events for brands such as Toyota, BMW and Berocca.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {BTA Active} % Organization
    {Sydney, Australia} % Location
    {Jan. 2013 - Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a cloud based travel management system using CakePHP and MySQL to automate manual tasks which saving hours of labor.}
        \item {Developed a cloud based insurance investigator management system using CakePHP to replace the old legacy system.}
        \item {Built custom websites for various businesses using Wordpress.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Network Engineer} % Job title
    {Bina Nusantara University} % Organization
    {Jakarta, Indonesia} % Location
    {Apr. 2009 - Sep. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed internal and external networks using Mikrotik and Cisco.}
        \item {Built a TV streaming server using Flash Media Server.}
        \item {Implemented operating system level virtualization using OpenVZ to reduce number of physical servers.}
        \item {Managed Linux and Unix servers.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
